Drivers of fish size in a changing climate

### 2017-10-05 draft.Rnw
fix evo figure
some changes

int_m <- 1000
int_t <- 500
int_temp <- 50

# Sluggish small
ss <- list(c=0.3,
           beta=0.15,
           delta=4,
           Ea=0.52, 
           gamma=40, 
           h=20, 
           k=1,
           lO=1, 
           m=10, 
           M=0.1 ,
           n=0.8, 
           O2crit=2, 
           omega=0.25, 
           p=0.75,
           P50=4.2, 
           phi=0.25, 
           q=0.75 ,
           shape=3,
           temp=seq(5,26,l=int_temp),
           Topt=20, 
           temp_ref=15,
           slope=-0.5,
           tmax=10,
           tr=0.5,
           v=6,
           lm=int_m,
           nu=-0.2,
           dt=int_t,
           min_m=-2,
           max_m= 1.5
)

# fast small
fs <- ss
fs$lO <- 2
fs$k <- 1.5
fs$h <- 40
#fs$v <- 2
#fs$M <- 0.8
fs$n <- 0.75
fs$p <- 0.70
fs$q <- 0.70

fl <- fs
fl$p <- 0.75
fl$q <- 0.75
#fl$nu <- -0.25
fl$tr <- 0.05
fl$tmax <- 40
fl$max_m <- 5

sl <- ss
sl$p <- 0.8
sl$q <- 0.8
#sl$nu <- -0.25
sl$tmax <- 40
sl$max_m <- 5
sl$tr <- 0.05

@@

gouts <- parallel::mclapply(scs,plot_data_growth_tO2,mc.cores = 4)

@@

cowplot::plot_grid(cp,np,nrow=2)
@

<<evo, fig.cap='On evolutionary time-scales, selection moves the reaction norm. Size-at-maturation reacts strongly to temperature changes in the model (left panel). Selection (S) induced changes in size are slow for M strategists, fast for P strategists.'>>=

>>>>

int_m <- 1000/2
int_t <- 1000/2
int_temp <- 50

# Sluggish small
ss <- list(c=0.3,
           beta=0.15,
           delta=4,
           Ea=0.52, 
           gamma=40, 
           h=20, 
           k=1,
           lO=1, 
           m=10, 
           n=0.85, 
           O2crit=2, 
           omega=0.25, 
           p=0.75,
           P50=4.2, 
           phi=0.25, 
           q=0.75 ,
           shape=3,
           temp=seq(5,26,l=int_temp),
           Topt=20, 
           temp_ref=15,
           slope=-0.3,
           tmax=15,
           tr=1,
           M=0.1,
           v=6,
           lm=int_m,
           nu=0.75-1,
           dt=int_t,
           min_m=-2,
           max_m= 2
)

# fast small
fs <- ss
fs$lO <- 2
fs$k <- 1.5
fs$h <- 40
fs$v <- 1
fs$M <- 1

fl <- fs
fl$n <- 0.8
fl$tr <- 0.2
fl$tmax <- 40
fl$max_m <- 4

sl <- ss
fl$n <- 0.8
sl$tmax <- 40
sl$max_m <- 4
sl$tr <- 0.2

@@

gouts <- parallel::mclapply(scs,plot_data_growth_tO2,mc.cores = 2)

@@

cowplot::plot_grid(cp,np,nrow=2,rel_heights = c(0.65,0.35))
@

<<evo, fig.cap='On evolutionary time-scales, selection moves the reaction norm. Size-at-maturation reacts strongly to temperature changes in the model (left panel). Selection (S) induced changes in size are slow for M strategists, fast for P strategists.',fig.height=4>>=
